Empowering the use of community driven preprints in ecology and evolution

### 2024-04-17 ms/ms.qmd
Fixing some code and package issue

# Load packages
#install.packages("pacman")
pacman::p_load(tidyverse, here, patchwork, readxl, MASS, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggrepel, ggimage, gt, performance, genderdata, gender, ggthemes, mapproj, DemografixeR, countrycode, see, glmmTMB, cowplot, viridis, cowplot)

@@

  #del_details <- delegates  %>% rename("attend" = "Attended hackathon (yes/no)") %>%
			mutate(attend = str_to_title(attend))  %>% tabyl(attend)

@@

# Seem to be missing the publication date for preprints and this should ne known for all
    data3 <- read_excel(here("data", "20231003_EER_preprints_metadata.xlsx"))  %>% clean_names()

	# Subset the relevant rows
		data3  <- data3  %>%  dplyr::select(preprint_id, preprint_doi, publisher_doi, published_date)  %>% rename("preprint_published_date" = "published_date" )

@@

  p1 <- ggplot(data2, aes(x = preprint_published_date.y)) +
    geom_histogram(fill = "black", color = "black") +
    labs(x = "Published Date", y = "Number of Papers") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) + theme(plot.tag = element_text(size = 16, face = "bold"), plot.tag.location = "margin")

@@

p1 <- preprints %>% ggplot(aes(x = time_between_preprint_and_pub_days)) + geom_histogram(binwidth = 30) + labs(x = "Days", y = "Frequency") + theme_classic()

@@

@@

p2 <- preprints  %>% ggplot(aes(x = is_oa)) + geom_bar() + labs(x = "Open Access", y = "Frequency") + theme_classic()

p3 <- preprints  %>% ggplot(aes(x = oa_status)) + geom_bar() + labs(x = "Open Access Status", y = "Frequency") + theme_classic()

p_pubsummary <- (p1 + p2) + plot_annotation(tag_levels = 'A', tag_suffix=")")

@@

##-------------------##
# Titel changes
##-------------------##
titles <- preprints %>%  filter(!is.na(publication_doi)) %>% tabyl(publication_title_changed)
```

>>>>

# Load packages
#install.packages("pacman")
remotes::install_github("lmullen/genderdata")
pacman::p_load(tidyverse, here, patchwork, readxl, MASS, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggrepel, ggimage, gt, performance, gender,genderdata, ggthemes, mapproj, DemografixeR, countrycode, see, glmmTMB, cowplot, viridis, cowplot)

@@

  #del_details <- delegates  %>% rename("attend" = "Attended hackathon (yes/no)") %>%
			#mutate(attend = str_to_title(attend))  %>% tabyl(attend)

@@

# Subset the relevant rows
		data3  <- data  %>%  dplyr::select(`Preprint ID`, `Preprint DOI`, `Published Date`)  %>% rename("preprint_pub_date" = "Published Date",
                                                                                                      "preprint_id"  = "Preprint ID")

@@

  p1 <- ggplot(data2, aes(x = preprint_pub_date)) +
    geom_histogram(fill = "black", color = "black") +
    labs(x = "Published Date", y = "Number of Papers") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) + theme(plot.tag = element_text(size = 16, face = "bold"), plot.tag.location = "margin")

@@

@@

p1_pub <- preprints %>% ggplot(aes(x = time_between_preprint_and_pub_days)) + geom_histogram(binwidth = 30) + geom_vline(aes(xintercept = sum_preprints$median), colour = "red", linetype = "dashed", linewidth = 1) + annotate("text", x = sum_preprints$median + 650, y = 60, label = paste0(sum_preprints$median, " days", "(~ ", sum_preprints$median/30, " months)"), size = 10, colour = "red") + labs(x = "Time to Publication (days)", y = "Number of Papers") + theme_classic() + theme(axis.title = element_text(size = 14))

@@

p2_pub <- preprints  %>% ggplot(aes(x = is_oa)) + geom_bar() + labs(x = "Open Access", y = "Number of Papers") + theme_classic() + theme(axis.title = element_text(size = 14))

p3_pub <- preprints  %>% ggplot(aes(x = oa_status)) + geom_bar() + labs(x = "Open Access Status", y = "Number of Papers") + theme_classic() + theme(axis.title = element_text(size = 14))

p_pubsummary <- (p1_pub + p2_pub + p3_pub) + plot_annotation(tag_levels = 'A', tag_suffix=")")
ggsave(p_pubsummary, filename = here("output", "figs", "pubsummary.png"), width = 20, height = 7)

@@

##-------------------##
# Title changes
##-------------------##
titles <- preprints %>%  filter(!is.na(publication_doi)) %>% tabyl(publication_title_changed)
```
